combine all centers pheno

### 2020-12-22 scripts/40_combine_all_samp_pheno.Rmd
update on the pheno cleaning again

I_phe <- bind_rows(
  I1 %>% 
    select(fid, pt_id = pid, timepoint:last_followup), 
  I2_pheno %>% 
    select(fid, pt_id, timepoint:last_followup)
) %>% 
  mutate(center = 'I')
```

@@

P_phe <- P_ %>% 
  left_join(P_ptb)  %>% 
  mutate(center = 'P') %>% 
  select(colnames(I_phe))
```

```{r}
# MSK
M_phe <- M %>% 
  mutate(center = 'M',
         pt_id = mrn) %>% 
  select(colnames(I_phe))
```

@@

all <- bind_rows(
  M_phe %>% mutate(pt_id = as.character(pt_id),
                   icansgrade = as.character(icansgrade)), 
  P_phe %>% 
    mutate(pt_id = as.character(pt_id)), 
  I_phe %>% 
    mutate(icansgrade = as.character(icansgrade))
) %>% 
  mutate(crsgrade = as.character(crsgrade))

>>>>

I_phe <- bind_rows(
  I1 %>% 
    select(fid, pt_id = pid, timepoint:last_followup), 
  I2_pheno %>% 
    select(fid, pt_id, timepoint:sampleid, oligoid:last_followup)
) %>% 
  mutate(center = 'I')
```

@@

P_phe <- P_ %>% 
  left_join(P_ptb)  %>% 
  mutate(center = 'P')

psamp <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/U Penn/samples/sample_mapping_UPenn.xlsx', sheet = 1) %>% 
  mutate(pt_id = pt_id-8000) %>% 
  filter(pt_id %in% P_phe$pt_id) %>% 
  full_join(P_phe) %>% 
  select(colnames(I_phe))
```

```{r}
# MSK
msamp <- readxl::read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/MSK/samples/sample_table_msk.xlsx', sheet = 1)
M_phe <- M %>% 
  mutate(timepoint = NA,
         oligoid = NA) %>% 
  mutate(center = 'M',
         pt_id = mrn) %>% 
  select(colnames(I_phe))
```

@@

all <- bind_rows(
  M_phe %>% mutate(pt_id = as.character(pt_id)), 
  psamp %>% 
    mutate(pt_id = as.character(pt_id)), 
  I_phe 
)
